Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-22 paper_jasa.tex
legend subscript updated
tweaking glossary

Table \ref{tbl:compare} illustrates the lineup protocol in relation to traditional hypothesis testing. Both start from the same place, the same null hypothesis. The classical test statistic is the $t$-statistic, where the parameter estimate is divided by its standard error. In the lineup, the test statistic is a plot of the data, here side-by-side boxplots are used, because the variable of interest is categorical and takes just two values. In traditional hypothesis testing the value of the test statistic is compared with all possible values of the sampling distribution, the distribution of the statistic if the null hypothesis is true. If it is extreme on this scale then the null hypothesis is rejected. In constrast in visual inference, the plot of the data is compared with plots of a finite number of samples drawn from the null distribution. If the data plot is selected as the most different, then this results in rejection of the null hypothesis.

>>>>

Table \ref{tbl:compare} illustrates the lineup protocol in relation to traditional hypothesis testing. Both start from the same place, the same null hypothesis. The classical test statistic is the $t$-statistic, where the parameter estimate is divided by its standard error. In the lineup protocol, the test statistic is a plot of the data, here side-by-side boxplots are used, because the variable of interest is categorical and takes just two values. In traditional hypothesis testing the value of the test statistic is compared with all possible values of the sampling distribution, the distribution of the statistic if the null hypothesis is true. If it is extreme on this scale then the null hypothesis is rejected. In constrast in visual inference, the plot of the data is compared with plots of a finite number of samples drawn from the null distribution. If the data plot is selected as the most different, then this results in rejection of the null hypothesis.
